A Walk In The Classroom - Using Fitbit Charge 4 to measure expert and novice teachers' heart rate and step counts in a laboratory study

### 2022-08-05 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
fitbit paper device description

## Material

>>>>

## Material
We used a Fitbit Charge 4 to measure the teachers' heart rate. The device was attached 2-finger widths above the ulnar styloid process to the partipant's wrist following the manufacturer’s instructions. To determine the heart rate, the Fitbit flashes green LEDs many times per second and uses light-sensitive photodiodes to measure the volume changes in the capillaries and then calculates how many times the heart beats per minute (bpm). Data were automatically wireless synced with an iPad via Bluetooth to a Fitbit account, and subsequently, the intraday second-by-second data were exported for each session using the opensource software Pulse Watch (PulseWatch. URL: https://iccir919.github.io/pulseWatch/public/index.html [accessed 2022-08-03]).
